---
title: "Process_OlisJazEmData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_OlisJazEmData.Rmd processes and combines BalticPhotoperiod_Imported_JazEmData.Rds from Data/ImportedData/ImportedJazEmData folder and BalticPhotoperiod_Imported_OlisData.Rds from Data/ImportedData/ImportedOlisData folder. This .Rmd generates BalticPhotoperiod_Processed_OlisSpectraAll.Rds and BalticPhotoperiod_Processed_OlisSpectraTidy.Rds (both stored in Data/ProcessedData/ProcessedOlisJazData folder) and 1 plot (stored in Output/Figures folder).

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 


library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggspectra)
library(ggpubr)
library(caret)
library(photobiologyWavebands)
library(reshape2)
library(photobiology)
library(gcookbook)

library(googledrive)
library(googlesheets4)
library(readxl)
library(tidyverse)
library(lubridate)
```

```{r set project variables}
Project <- "BalticPhotoperiod"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData")
DataInOlis <- file.path("..", "Data", "ImportedData", "ImportedOlisData", fsep = .Platform$file.sep)
DataInJaz <- file.path("..", "Data", "ImportedData", "ImportedJazEmData", fsep = .Platform$file.sep)

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read imported Olis and Jaz files

```{r exported Rmd only first time in session}
list.files(path = DataInOlis, pattern = Project, full.names = TRUE)
list.files(path = DataInJaz, pattern = Project, full.names = TRUE)
```

```{r read imported Olis file}
OLISSpectraFile <- "../Data/ImportedData/ImportedOlisData/BalticPhotoperiod_Imported_OlisData.Rds"
OLISSpectraFileName <- str_split(string = OLISSpectraFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
OLISSpectra <- readRDS(OLISSpectraFile)  %>%
  ungroup()

JazFile <- "../Data/ImportedData/ImportedJazEmData/BalticPhotoperiod_Imported_JazEmData.Rds"
JazFileName <- str_split(string = JazFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
JazData <- readRDS(JazFile)  %>%
  ungroup()
```

# Preparing df for further analysis

```{r}
JazData<-JazData %>% 
  filter(WL == "WW") %>% 
  filter(MC == "MC257") %>% 
  select(-c(MCMeasuredPar_uE, MCSetPar_uE))
```

# Normalize Jaz emission to 439 nm

```{r Normalization Jaz emission at 439}
EmissionJazWW <- JazData %>%
  #group_by(WL) %>%
  filter(MCEm_nm == 439) %>%
  mutate(EmJaz439 = Emission) %>%
  select(EmJaz439) 
  # ungroup()
JazDataRoundMeta <- JazData %>%
  cross_join(., EmissionJazWW) %>%
  mutate(EmNormJaz439 = Emission / EmJaz439)

rm(EmissionJazWW)
```

# Remove unrevelant columns 

```{r}
JazDataRoundMeta<-JazDataRoundMeta %>% 
  select(-c(MC, WL, ObsDateJaz))
```

# Merge Olis and Jaz data

```{r combine Olis spectra and Jaz data}
OLISSpectraMeta <- OLISSpectra %>%
  left_join(., JazDataRoundMeta, by = c("nm" = "MCEm_nm")) %>%
  unique()
```

# Estimate PUR

```{r estimate PUR}
OLISSpectraMetaPUR <- OLISSpectraMeta %>%
  mutate(PURNorm = (AbsNorm440*EmNormJaz439)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz439 = sum(EmNormJaz439)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz439)) %>% 
  ungroup() 
```

# Calculate daily PUR photon dose and PUR/PAR ratio

```{r calculate PUR Photon dose}
OLISSpectraMetaPUR1 <- OLISSpectraMetaPUR %>%
  filter(Photoperiod != "24") %>% 
  mutate(PURPhotonDose_day =(PUR/2)*Photoperiod*3600)

OLISSpectraMetaPUR2 <- OLISSpectraMetaPUR %>%
  filter(Photoperiod == "24") %>% 
  mutate(PURPhotonDose_day = PUR*Photoperiod*3600)
  
OLISSpectraMetaPUR <-rbind(OLISSpectraMetaPUR1, OLISSpectraMetaPUR2)
  rm(OLISSpectraMetaPUR1,OLISSpectraMetaPUR2)

OLISSpectraMetaPUR <-OLISSpectraMetaPUR %>% 
  mutate(PURPARRatio = PUR/Par_ue)  
```

# Filter unrevelant data

```{r filter unrevelant data}
OLISSpectraMetaPUR<-OLISSpectraMetaPUR %>% 
  filter(PUR>=0) %>% 
  filter(PUR<=900)
```

# Preparing df for creating representative plot

```{r preparing selected data for creating representative plot}
OLISSpectraMetaPURShortBA127R<- OLISSpectraMetaPUR %>%
  filter(Photoperiod == "12") %>% 
  filter(Strain == "BA127R") %>% 
  filter(Par_ue == 300) %>% 
  filter(E_days == "4" | E_days == "8") %>% 
  mutate(E_days=case_when(E_days==4~3,
         E_days==8~7)) %>% 
  mutate(PURNormBA127R = PURNorm) %>% 
  select(-c(PURNorm, FilenameJaz, FilenameOlis))

OLISSpectraMetaPURShortBA77G<- OLISSpectraMetaPUR %>%
  filter(Photoperiod == "12") %>% 
  filter(Strain == "BA77G") %>% 
  filter(Par_ue == 300) %>% 
  filter(E_days == "3" | E_days == "7") %>% 
  mutate(PURNormBA77G = PURNorm) %>% 
  select(-c(PURNorm, FilenameJaz, FilenameOlis))

OLISSpectraMetaPURShort <- OLISSpectraMetaPURShortBA127R %>%
  full_join(., OLISSpectraMetaPURShortBA77G, by = c("SampleID" = "SampleID", "Run" = "Run", "Strain" = "Strain", "ExpDate" = "ExpDate", "Par_ue" = "Par_ue", "Photoperiod" = "Photoperiod", "MC"="MC", "Tube" = "Tube", "O2" = "O2", "WL" = "WL", "LightShape" = "LightShape", "ExpEndDate"="ExpEndDate", "nm" = "nm", "ObsDate" = "ObsDate", "Absorbance" = "Absorbance", "SumAb" = "SumAb", "Abs440" = "Abs440", "AbsNorm440" = "AbsNorm440", "SumAbNorm" = "SumAbNorm", "E_days" = "E_days", "Emission" = "Emission", "EmJaz439" = "EmJaz439", "EmNormJaz439" = "EmNormJaz439", "PURNormSum" = "PURNormSum", "SumEmNormJaz439" = "SumEmNormJaz439", "PUR" = "PUR", "PURPhotonDose_day" = "PURPhotonDose_day", "PARPhotonDose_day" = "PARPhotonDose_day")) 
```

```{r Changes strain names}
OLISSpectraMetaPURShort <- OLISSpectraMetaPURShort %>%
      mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))
```

# Create plot

```{r Create plot, fig.height = 10, fig.width = 8}
Par_ue.labs <- c("30 µE", "90 µE", "180 µE", "Phase of growth", "900 µE")
names(Par_ue.labs) <- c("30", "90", "180", "300", "900")

Photoperiod.labs <- c("8 h", "Photoperiod: 12 h", "16 h", "24 h")
names(Photoperiod.labs) <- c("8", "12", "16", "24")

E_days.labs <- c("Exponential", "Pre-stationary")
names(E_days.labs) <- c("3", "7")

Strain.labs <- c("PC-rich", "PE-rich")
names(Strain.labs) <- c("PC-rich_077", "PE-rich_127")

O2.labs <- c("Strain")
names(O2.labs) <- c(21)

data_textPUR0 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PAR = 300 µE', 'PAR = 300 µE'))
data_textPUR00 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PC-rich_077", "PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PAR = 300 µE', 'PAR = 300 µE'))
data_textPUR1 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PUR = 176 µE', 'PUR = 129 µE'))
data_textPUR2 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PC-rich_077", "PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PUR = 139 µE', 'PUR = 128 µE'))

data_textpigment1 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 440 nm'))
data_textpigment3 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 680 nm'))
data_textpigment4 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PC 620 nm'))
data_textpigment5 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Car 480 nm'))
data_textpigment6 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PUB 500 nm'))

arrowdf1 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf3 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf4 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf5 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf6 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))

data_textpigment7 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 440 nm'))
data_textpigment8 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Car 480 nm'))
data_textpigment9 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PE 570 nm'))
data_textpigment10 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 680 nm'))
data_textpigment11 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PC 620 nm'))
data_textpigment12 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PUB 500 nm'))

arrowdf7 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf8 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf9 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf10 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf11 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf12 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))

OLISSpectraMetaPURShort %>%
  filter(Photoperiod == "12") %>%
  filter(Strain == "PC-rich_077" | Strain == "PE-rich_127") %>%
  filter(Par_ue == 300) %>%
  filter(E_days == "3" | E_days == "7") %>%
  ggplot() +

  geom_area(aes(x = nm, y = EmNormJaz439, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = PURNormBA127R, fill = "brown4"), alpha = 0.5, show.legend = F) +
  geom_area(aes(x = nm, y = PURNormBA77G, fill = "palegreen3"), alpha = 0.5, show.legend = F) +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F, linewidth = 0.4) +

  geom_text(data=data_textPUR0, aes(x=450, y=1.26, label=label), size=3.7) +
  geom_text(data=data_textPUR00, aes(x=450, y=1.26, label=label), size=3.7) +
  geom_text(data=data_textPUR1, aes(x=450, y=1.21, label=label), size=3.7) +
  geom_text(data=data_textPUR2, aes(x=450, y=1.21, label=label), size=3.7) +

  geom_text(data=data_textpigment1, aes(x=500, y=1.1, label=label), size=4, colour = "darkgreen") + #chla440
  geom_text(data=data_textpigment5, aes(x=500, y=0.8, label=label), size=4, colour = "orange") + #Car
  geom_text(data=data_textpigment3, aes(x=650, y=1.2, label=label), size=4, colour = "darkgreen") +#chla680
  geom_text(data=data_textpigment4, aes(x=590, y=0.95, label=label), size=4, colour = "deepskyblue4") + #PC
  geom_text(data=data_textpigment6, aes(x=485, y=0.25, label=label), size=4, colour = "sienna4") + #PUB
  geom_segment(data = arrowdf1,
               aes(x = 480, xend = 445, y = 1.05, yend = 1),
               colour = "darkgreen", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
  geom_segment(data = arrowdf5,
               aes(x = 480, xend = 475, y = 0.75, yend = 0.54),
               colour = "orange", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
  geom_segment(data = arrowdf3,
               aes(x = 660, xend = 680, y = 1.14, yend = 0.95),
               colour = "darkgreen", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
  geom_segment(data = arrowdf4,
               aes(x = 610, xend = 630, y = 0.90, yend = 0.82),
               colour = "deepskyblue4", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
  geom_segment(data = arrowdf4,
               aes(x = 480, xend = 494, y = 0.30, yend = 0.41),
               colour = "sienna4", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
  geom_text(data=data_textpigment7, aes(x=500, y=1.1, label=label), size=4, colour = "darkgreen") + #chla440
  geom_text(data=data_textpigment8, aes(x=500, y=0.8, label=label), size=4, colour = "orange") + #Car
  geom_text(data=data_textpigment9, aes(x=580, y=1.0, label=label), size=4, colour = "darkmagenta") + #PE
  geom_text(data=data_textpigment10, aes(x=650, y=1.2, label=label), size=4, colour = "darkgreen") +#chla680
  geom_text(data=data_textpigment11, aes(x=600, y=0.17, label=label), size=4, colour = "deepskyblue4") + #PC
  geom_text(data=data_textpigment12, aes(x=495, y=0.30, label=label), size=4, colour = "sienna4") + #PUB
  geom_segment(data = arrowdf7,
               aes(x = 480, xend = 445, y = 1.05, yend = 1),
               colour = "darkgreen", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
  geom_segment(data = arrowdf8,
               aes(x = 480, xend = 475, y = 0.75, yend = 0.55),
               colour = "orange", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
  geom_segment(data = arrowdf9,
               aes(x = 590, xend = 575, y = 0.95, yend = 0.85),
               colour = "darkmagenta", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PE
  geom_segment(data = arrowdf10,
               aes(x = 660, xend = 680, y = 1.14, yend = 0.85),
               colour = "darkgreen", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
  geom_segment(data = arrowdf11,
               aes(x = 610, xend = 630, y = 0.2, yend = 0.3),
               colour = "deepskyblue4", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
  geom_segment(data = arrowdf12,
               aes(x = 490, xend = 500, y = 0.35, yend = 0.52),
               colour = "sienna4", size = 0.5, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
  scale_color_manual(values = c("PC-rich_077" ="palegreen3", "PE-rich_127" ="brown4")) +
  scale_linetype_manual(values = c("PC-rich_077" ="solid", "PE-rich_127" ="longdash")) +
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  labs(y = "Normalized whole-cell absorbance, lamp emission, and PUR", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c (-0.01, 1.25)) +
  ggh4x::facet_nested(cols = vars(Par_ue, E_days), rows = vars(O2, Strain),labeller = labeller(Ex_WL = label_both, WL = label_both, E_days = E_days.labs, Photoperiod = Photoperiod.labs, Par_ue = Par_ue.labs, Strain = Strain.labs, O2 = O2.labs, )) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.title = element_blank(),
        legend.direction="horizontal",
        legend.position = c(0.08,0.97),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text.align = 0,
        legend.key.width= unit(0.3, 'cm'),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_OlisSpectra",".png",sep = "")), height=9, width= 9,  dpi = 300, limitsize = TRUE)
```

```{r Create plot, fig.height = 6, fig.width = 8}

Par_ue.labs <- c("30 µE", "90 µE", "180 µE", "Phase of growth", "900 µE")
names(Par_ue.labs) <- c("30", "90", "180", "300", "900")

Photoperiod.labs <- c("8 h", "Photoperiod: 12 h", "16 h", "24 h")
names(Photoperiod.labs) <- c("8", "12", "16", "24")

E_days.labs <- c("Exponential", "Pre-stationary")
names(E_days.labs) <- c("3", "7")

Strain.labs <- c("PE-rich_127", "PC-rich_077")
names(Strain.labs) <- c("PE-rich_127", "PC-rich_077")

data_textPUR0 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PAR = 300 µE', 'PAR = 300 µE'))

data_textPUR1 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PUR (PE-rich) = 176 µE', 'PUR (PE-rich) = 129 µE'))

data_textPUR2 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PUR (PC-rich) = 139 µE', 'PUR (PC-rich) = 128 µE'))

data_textpigment1 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Chl a 440 nm'))
data_textpigment2 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PE 570 nm'))
data_textpigment3 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Chl a 680 nm'))
data_textpigment4 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PC 620 nm'))
data_textpigment5 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Car 480 nm'))
data_textpigment6 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PUB 500 nm'))

arrowdf1 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf2 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf3 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf4 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf5 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf6 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)


OLISSpectraMetaPURShort %>%
  filter(Photoperiod == "12") %>%
  filter(Strain == "PE-rich_127" | Strain == "PC-rich_077") %>%
  filter(Par_ue == 300) %>%
  filter(E_days == "3" | E_days == "7") %>%
  ggplot() +
  geom_area(aes(x = nm, y = EmNormJaz439, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = PURNormBA127R, fill = "brown4"), alpha = 0.5, show.legend = F) +
  geom_area(aes(x = nm, y = PURNormBA77G, fill = "palegreen3"), alpha = 0.5, show.legend = F) +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F, linewidth = 0.5) +

  geom_text(data=data_textPUR0, aes(x=437, y=1.26, label=label), size=3.5) +
  geom_text(data=data_textPUR1, aes(x=465, y=1.21, label=label), size=3.5) +
  geom_text(data=data_textPUR2, aes(x=465, y=1.16, label=label), size=3.5) +

  geom_text(data=data_textpigment1, aes(x=450, y=1.07, label=label), size=4, colour = "darkgreen") + #chla440
  geom_text(data=data_textpigment5, aes(x=430, y=0.36, label=label), size=4, colour = "coral3") + #Car
  geom_text(data=data_textpigment2, aes(x=520, y=0.92, label=label), size=4, colour = "darkmagenta") + #PE
  geom_text(data=data_textpigment3, aes(x=660, y=1.08, label=label), size=4, colour = "darkgreen") +#chla680
  geom_text(data=data_textpigment4, aes(x=605, y=1.0, label=label), size=4, colour = "deepskyblue4") + #PC
  geom_text(data=data_textpigment6, aes(x=485, y=0.08, label=label), size=4, colour = "sienna4") + #PUB

  geom_segment(data = arrowdf1,
               aes(x = 470, xend = 440, y = 1.04, yend = 1.02),
               colour = "darkgreen", size = 0.7, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
  geom_segment(data = arrowdf5,
               aes(x = 450, xend = 470, y = 0.4, yend = 0.5),
               colour = "coral3", size = 0.7, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
  geom_segment(data = arrowdf2,
               aes(x = 538, xend = 568, y = 0.88, yend = 0.86),
               colour = "darkmagenta", size = 0.7, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PE
  geom_segment(data = arrowdf3,
               aes(x = 697, xend = 680, y = 1.05, yend = 0.92),
               colour = "darkgreen", size = 0.7, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
  geom_segment(data = arrowdf4,
               aes(x = 632, xend = 630, y = 0.95, yend = 0.82),
               colour = "deepskyblue4", size = 0.7, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
  geom_segment(data = arrowdf4,
               aes(x = 465, xend = 500, y = 0.12, yend = 0.52),
               colour = "sienna4", size = 0.7, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
  scale_color_manual(values = c("PE-rich_127" ="brown4", "PC-rich_077" ="palegreen3")) +
  scale_linetype_manual(values = c("PE-rich_127" ="longdash", "PC-rich_077" ="solid")) +
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) + 
  scale_fill_identity() +
  labs(y = "Normalized whole-cell absorbance, lamp emission, and PUR", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c (-0.01, 1.25)) +
  ggh4x::facet_nested(cols = vars(Par_ue, E_days), labeller = labeller(Ex_WL = label_both, WL = label_both, E_days = E_days.labs, Photoperiod = Photoperiod.labs, Par_ue = Par_ue.labs, Strain = Strain.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.title = element_blank(),
        legend.direction="horizontal",
        legend.position = c(0.08,0.97),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text.align = 0,
        legend.key.width= unit(0.3, 'cm'),
        legend.text = element_text(size=10))
```
```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_OlisSpectra2",".png",sep = "")), height=6, width= 8,  dpi = 300, limitsize = TRUE)
```

------------------------------------------ new idea for merging plot together with PUR/PAR ratio

# Preparing df for creating representative plot

```{r preparing selected data for creating representative plot}
OLISSpectraMetaPURSS<-OLISSpectraMetaPUR %>% 
  select(-c(ExpDate, Run, Tube, MC, LightShape, ExpEndDate, FilenameOlis, FilenameJaz, ObsDate)) %>% 
  filter(PARPhotonDose_day == 432000 | PARPhotonDose_day == 17280000) 
    
OLISExp056<- OLISSpectraMetaPURSS %>%
  filter(Strain == "BA56G")  %>% 
  filter(E_days ==3)
OLISExp056$Phase <-"Exponential"
OLISExp056$Photon <-"Low"

OLISSt056<- OLISSpectraMetaPURSS %>%
  filter(Strain == "BA56G")  %>% 
  filter(E_days ==5 | E_days == 12)
OLISSt056$Phase <-"Pre-stationary"
OLISSt056$Photon <-"High"

OLIS056<-rbind(OLISExp056, OLISSt056)  
    #mutate(PURNormBA56G = PURNorm)


OLISExp077<- OLISSpectraMetaPURSS %>%
  filter(Strain == "BA77G")  %>% 
  filter(E_days ==3)
OLISExp077$Phase <-"Exponential"
OLISExp077$Photon <-"Low"

OLISSt077<- OLISSpectraMetaPURSS %>%
  filter(Strain == "BA77G")  %>% 
  filter(E_days ==5 | E_days == 12)
OLISSt077$Phase <-"Pre-stationary"
OLISSt077$Photon <-"High"

OLIS077<-rbind(OLISExp077, OLISSt077) 
  #mutate(PURNormBA77G = PURNorm)


OLISExp048<- OLISSpectraMetaPURSS %>%
  filter(Strain == "BA48R")  %>% 
  filter(E_days ==4)
OLISExp048$Phase <-"Exponential"
OLISExp048$Photon <-"Low"

OLISSt048<- OLISSpectraMetaPURSS %>%
  filter(Strain == "BA48R")  %>% 
  filter(E_days ==5 | E_days == 14)
OLISSt048$Phase <-"Pre-stationary"
OLISSt048$Photon <-"High"

OLIS048<-rbind(OLISExp048, OLISSt048)  
    #mutate(PURNormBA48R = PURNorm)


OLISExp127<- OLISSpectraMetaPURSS %>%
  filter(Strain == "BA127R")  %>% 
  filter(E_days ==4)
OLISExp127$Phase <-"Exponential"
OLISExp127$Photon <-"Low"

OLISSt127<- OLISSpectraMetaPURSS %>%
  filter(Strain == "BA127R")  %>% 
  filter(E_days ==5 | E_days == 14)
OLISSt127$Phase <-"Pre-stationary"
OLISSt127$Photon <-"High"

OLIS127<-rbind(OLISExp127, OLISSt127) 
    #mutate(PURNormBA127R = PURNorm)


OLIS<-rbind(OLIS056, OLIS077, OLIS048, OLIS127) 




# OLISSpectraMetaPURShortBA77G<- OLISSpectraMetaPUR %>%
#   filter(Photoperiod == "12") %>% 
#   filter(Strain == "BA77G") %>% 
#   filter(Par_ue == 300) %>% 
#   filter(E_days == "3" | E_days == "7") %>% 
#   mutate(PURNormBA77G = PURNorm) %>% 
#   select(-c(PURNorm, FilenameJaz, FilenameOlis))
# 
# OLISSpectraMetaPURShort <- OLISSpectraMetaPURShortBA127R %>%
#   full_join(., OLISSpectraMetaPURShortBA77G, by = c("SampleID" = "SampleID", "Run" = "Run", "Strain" = "Strain", "ExpDate" = "ExpDate", "Par_ue" = "Par_ue", "Photoperiod" = "Photoperiod", "MC"="MC", "Tube" = "Tube", "O2" = "O2", "WL" = "WL", "LightShape" = "LightShape", "ExpEndDate"="ExpEndDate", "nm" = "nm", "ObsDate" = "ObsDate", "Absorbance" = "Absorbance", "SumAb" = "SumAb", "Abs440" = "Abs440", "AbsNorm440" = "AbsNorm440", "SumAbNorm" = "SumAbNorm", "E_days" = "E_days", "Emission" = "Emission", "EmJaz439" = "EmJaz439", "EmNormJaz439" = "EmNormJaz439", "PURNormSum" = "PURNormSum", "SumEmNormJaz439" = "SumEmNormJaz439", "PUR" = "PUR", "PURPhotonDose_day" = "PURPhotonDose_day", "PARPhotonDose_day" = "PARPhotonDose_day")) 
```

```{r Changes strain names}
OLISSpectraMetaPURShort <- OLIS %>%
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) %>% 
    mutate(Phase2=case_when(Par_ue==30~"Exponential",
         Par_ue==600~"Pre-stationary"))
OLISSpectraMetaPURShort$facetsPhase<-"Phase~of~growth"
OLISSpectraMetaPURShort$facetsStrain<-"Strain"

OLISSpectraMetaPURShort56<-OLISSpectraMetaPURShort %>% 
  filter(Strain=="PC-rich_056") %>% 
  filter(Photon=="Low") %>% 
  mutate(PURNorm56 = PURNorm) %>% 
  mutate(Phase2=case_when(Par_ue==30~"Exponential",
         Par_ue==600~"Pre-stationary"))
OLISSpectraMetaPURShort56$facetsPhase<-"Phase~of~growth"
OLISSpectraMetaPURShort56$facetsStrain<-"Strain"

OLISSpectraMetaPURShort77<-OLISSpectraMetaPURShort %>% 
  filter(Strain=="PC-rich_077") %>% 
  filter(Photon=="Low") %>% 
  mutate(PURNorm77 = PURNorm) %>% 
  mutate(Phase2=case_when(Par_ue==30~"Exponential",
         Par_ue==600~"Pre-stationary"))
OLISSpectraMetaPURShort77$facetsPhase<-"Phase~of~growth"
OLISSpectraMetaPURShort77$facetsStrain<-"Strain"

OLISSpectraMetaPURShort48<-OLISSpectraMetaPURShort %>% 
  filter(Strain=="PE-rich_048") %>% 
  filter(Photon=="Low") %>% 
  mutate(PURNorm48 = PURNorm) %>% 
  mutate(Phase2=case_when(Par_ue==30~"Exponential",
         Par_ue==600~"Pre-stationary"))
OLISSpectraMetaPURShort48$facetsPhase<-"Phase~of~growth"
OLISSpectraMetaPURShort48$facetsStrain<-"Strain"

OLISSpectraMetaPURShort127<-OLISSpectraMetaPURShort %>% 
  filter(Strain=="PE-rich_127") %>% 
  filter(Photon=="Low") %>% 
  mutate(PURNorm127 = PURNorm) %>% 
  mutate(Phase2=case_when(Par_ue==30~"Exponential",
         Par_ue==600~"Pre-stationary"))
OLISSpectraMetaPURShort127$facetsPhase<-"Phase~of~growth"
OLISSpectraMetaPURShort127$facetsStrain<-"Strain"
```





# Create plot

```{r Create plot, fig.height = 8, fig.width = 8, warning = FALSE}
data_textB <- data.frame(facetsPhase = c("Phase~of~growth"), Phase2 = c("Exponential"), facetsStrain  = c("Strain"), Strain  = c("PC-rich_056"), label = c('B'))

# k_data056 = data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056"))
# k_data077 = data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_077"))
# k_data048 = data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PE-rich_048"))
# k_data127 = data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PE-rich_127"))


Spectra<-OLISSpectraMetaPURShort %>%
    filter(Photon=="Low") %>% 
  ggplot() +
  geom_area(aes(x = nm, y = EmNormJaz439, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = PURNorm56, fill = "seagreen4"), alpha = 0.5, show.legend = F, OLISSpectraMetaPURShort56) +
  geom_area(aes(x = nm, y = PURNorm77, fill = "palegreen3"), alpha = 0.5, show.legend = F, OLISSpectraMetaPURShort77) +
  geom_area(aes(x = nm, y = PURNorm48, fill = "brown1"), alpha = 0.5, show.legend = F, OLISSpectraMetaPURShort48) +
  geom_area(aes(x = nm, y = PURNorm127, fill = "brown4"), alpha = 0.5, show.legend = F, OLISSpectraMetaPURShort127) +
  
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain)), show.legend = F, linewidth = 0.4) +
  
  geom_text(data=data_textB, aes(x=410, y=1.5, label=label), size=6) +
  
  # geom_segment(data = k_data056, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "seagreen4", size = 6, alpha = 0.3) +
  # geom_segment(data = k_data077, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "palegreen3", size = 6, alpha = 0.3) +
  # geom_segment(data = k_data048, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "brown1", size = 6, alpha = 0.3) +
  # geom_segment(data = k_data127, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "brown4", size = 6, alpha = 0.3) +
  
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="") +
  # scale_linetype_manual(values = c("PC-rich_077" ="solid", "PE-rich_127" ="longdash")) +
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  labs(y = "Normalized whole-cell absorbance, lamp emission, and PUR", x = "Wavelength (nm)") +
  # scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  # coord_cartesian(ylim = c (-0.01, 1.25)) +
  ggh4x::facet_nested(cols = vars(facetsPhase, Phase2), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
    #ggh4x::facet_nested(cols = vars(Photon), rows = vars(Strain)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(vjust = -1), 
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10), vjust = -1),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.85,0.88),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        legend.title = element_blank(),
        legend.text = element_text(size=11))
Spectra
```





# Cleaning df before saving as Rds and removed unnecessary files from the environment

```{r delete unused df from the environment}
rm(data_textpigment1,data_textpigment2,data_textpigment3,data_textpigment4,data_textpigment5,data_textpigment6, data_textpigment7, data_textpigment8, data_textpigment9, data_textpigment10, data_textpigment11, data_textpigment12, arrowdf1,arrowdf2,arrowdf3,arrowdf4,arrowdf5,arrowdf6, arrowdf7, arrowdf8, arrowdf9, arrowdf10, arrowdf11, arrowdf12, data_textPUR0, data_textPUR00, data_textPUR1,data_textPUR2, JazData, JazDataRoundMeta, OLISSpectraMetaPURShortBA127R, OLISSpectraMetaPURShortBA77G, OLISSpectraMeta, OLISSpectra)
```

# Preparing df for creating plot - added proper strain names and facet labels

```{r create tidy PAR photon dose and facets for plot}
OLISSpectraMetaPUR <- OLISSpectraMetaPUR %>%
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))
OLISSpectraMetaPUR$facetsPar_ue = factor(OLISSpectraMetaPUR$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
OLISSpectraMetaPUR$facetsPhotoperiod = factor(OLISSpectraMetaPUR$WL, labels = c("Photoperiod~(h)"))
OLISSpectraMetaPUR$facetsStrain = factor(OLISSpectraMetaPUR$WL, labels = c("Strain"))
OLISSpectraMetaPUR$facetsPhase = factor(OLISSpectraMetaPUR$WL, labels = c("Phase~of~growth"))
```

# Load tmaxAG catalog 

```{r}
gs4_deauth()
tmaxAG<- read_sheet("https://docs.google.com/spreadsheets/d/1ksY7xlg9wOsICOBRmZkHPKdd9KOislNwPDzyuJ3UIUI/edit#gid=0")
as.data.frame(tmaxAG)
tmaxAG <- tmaxAG

tmaxAG<-tmaxAG %>% 
  mutate(Par_ue = as.numeric(Par_ue)) %>%
  mutate(Photoperiod = as.numeric(Photoperiod)) %>%
  mutate(tMaxAG = as.numeric(tMaxAG)) %>%
  mutate(dayRound_tmaxAG=tMaxAG/24) %>% 
  mutate(dayRound_tmaxAG = round(dayRound_tmaxAG, digits = 0)) %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))

tmaxAG$facetsPar_ue = factor(tmaxAG$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
tmaxAG$facetsPhotoperiod = factor(tmaxAG$WL, labels = c("Photoperiod~(h)"))
tmaxAG$facetsStrain = factor(tmaxAG$O2, labels = c("Strain"))
tmaxAG$facetsPARPhotonDose_day = factor(tmaxAG$WL, labels = c("PAR~photon~dose~(10^{5}~µmol~photons~m^{-2}~d^{-1})"))

tmaxAGno24<-tmaxAG %>% 
  filter(Photoperiod != "24") %>% 
  mutate(PARPhotonDose_day =(Par_ue/2)*Photoperiod*3600)
tmaxAG24<-tmaxAG %>% 
  filter(Photoperiod == "24") %>% 
  mutate(PARPhotonDose_day = Par_ue*Photoperiod*3600) 
tmaxAG <-rbind(tmaxAGno24, tmaxAG24)
  rm(tmaxAGno24, tmaxAG24)
```

# Merge OlisJaz data and tMaxAG to divide spectra from exponential and pre-stationary phase

```{r Combine pigment and tMaxAG df}
OLISSpectraMetaPURMaxAG <- OLISSpectraMetaPUR %>%
  left_join(., tmaxAG, by = c("Strain"="Strain","Par_ue"="Par_ue","Photoperiod"="Photoperiod", "WL"="WL", "O2"="O2", "PARPhotonDose_day"="PARPhotonDose_day", "facetsPar_ue"="facetsPar_ue", "facetsPhotoperiod"="facetsPhotoperiod", "facetsStrain" = "facetsStrain"))
```

# Divided pigments data to Exponential and Pre-stationary phase according to tmaxAG

```{r divided pigments data to Exponential and Pre-stationary}
OLISSpectraMetaPURMaxAG <- OLISSpectraMetaPURMaxAG %>%
  mutate(Phase = O2) %>%
  mutate(Phase=case_when(E_days<=dayRound_tmaxAG~"Exponential",
         E_days>dayRound_tmaxAG~"Pre-stationary")) 
```

# Choose selected spectra - for plot only

```{r}
OLISSelect <-OLISSpectraMetaPURMaxAG %>%
  filter(Run == 50) %>% 
  filter(E_days == 1) %>% 
  select(-c(Phase))
OLISSelect$Phase <- 'Exponential'

OLISSelectBA56Exp <-OLISSpectraMetaPURMaxAG %>%
  filter(Strain == "PC-rich_056") %>% 
  filter(E_days == 3 & Par_ue == 30 & Photoperiod == 12) 
OLISSelectBA77Exp <-OLISSpectraMetaPURMaxAG %>%
  filter(Strain == "PC-rich_077") %>% 
  filter(E_days == 4 & Par_ue == 30 & Photoperiod == 16) 
OLISSelectBA48Exp <-OLISSpectraMetaPURMaxAG %>%
  filter(Strain == "PE-rich_048") %>% 
  filter(E_days == 2 & Par_ue == 30 & Photoperiod == 8) 
OLISSelectBA127Exp <-OLISSpectraMetaPURMaxAG %>%
  filter(Strain == "PE-rich_127") %>% 
  filter(E_days == 2 & Par_ue == 300 & Photoperiod == 12) 

OLISSelectBA56St <-OLISSpectraMetaPURMaxAG %>%
  filter(Strain == "PC-rich_056") %>% 
  filter(E_days == 7 & Par_ue == 900 & Photoperiod == 8) 
OLISSelectBA77St <-OLISSpectraMetaPURMaxAG %>%
  filter(Strain == "PC-rich_077") %>% 
  filter(E_days == 7 & Par_ue == 900 & Photoperiod == 8) 
OLISSelectBA48St <-OLISSpectraMetaPURMaxAG %>%
  filter(Strain == "PE-rich_048") %>% 
  filter(E_days == 14 & Par_ue == 30 & Photoperiod == 12) 
OLISSelectBA127St <-OLISSpectraMetaPURMaxAG %>%
  filter(Strain == "PE-rich_127") %>% 
  filter(E_days == 14 & Par_ue == 30 & Photoperiod == 12) 

OLISSelectStrains<-rbind(OLISSelectBA56Exp, OLISSelectBA77Exp, OLISSelectBA48Exp, OLISSelectBA127Exp, OLISSelectBA56St, OLISSelectBA77St, OLISSelectBA48St, OLISSelectBA127St)

rm(OLISSelectBA56Exp, OLISSelectBA77Exp, OLISSelectBA48Exp, OLISSelectBA127Exp, OLISSelectBA56St, OLISSelectBA77St, OLISSelectBA48St, OLISSelectBA127St)
```

# Testing max peak condition

```{r}
# Test<-OLISSpectraMetaPURMaxAG %>% 
#   filter(Strain == "PE-rich_127") %>% 
#   filter(Phase == "Pre-stationary")
```

# Create preliminary plot

```{r preliminary plot}
# data_text_Exp<- data.frame(WL = c("WW", "WW"), facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('Max peak - day 3, 30 µE, 12 h', 'Max peak - day 4, 30 µE, 16 h', 'Max peak - day 2, 30 µE, 8 h', 'Max peak - day 2, 300 µE, 12 h'))
# 
# data_text_St<- data.frame(WL = c("WW", "WW"), facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('Max peak - day 7, 900 µE, 8 h', 'Max peak - day 7, 900 µE, 8 h', 'Max peak - day 14, 30 µE, 12 h', 'Max peak - day 14, 30 µE, 12 h'))

data_text_Exp<- data.frame(WL = c("WW", "WW"), facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('Max peak: day 3', 'Max peak: day 4', 'Max peak: day 2', 'Max peak: day 2'))
data_text_St<- data.frame(WL = c("WW", "WW"), facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('Max peak: day 7', 'Max peak: day 7', 'Max peak: day 14', 'Max peak: day 14'))

data_text_Exp1<- data.frame(WL = c("WW", "WW"), facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('30 µE, 12 h', '30 µE, 16 h', '30 µE, 8 h', ' 300 µE, 12 h'))
data_text_St1<- data.frame(WL = c("WW", "WW"), facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('900 µE, 8 h', '900 µE, 8 h', '30 µE, 12 h', '30 µE, 12 h'))

lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))

OLISSpectraMetaPURMaxAG %>%
  filter(Phase == "Exponential" | Phase == "Pre-stationary") %>% 
  filter(E_days != 1) %>% 
  ggplot() +
  geom_area(aes(x = nm, y = EmNormJaz439), fill = "gray84", alpha = 0.6, show.legend = F) +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain)), show.legend = F, linewidth = 0.7,  alpha = 0.5) +
  
  geom_line(aes(x = nm, y = AbsNorm440), show.legend = F, linewidth = 0.5,  colour = "gray20", alpha = 0.7, OLISSelect) +
  geom_line(aes(x = nm, y = AbsNorm440), show.legend = F, linewidth = 0.5,  colour = "blue", alpha = 0.7, OLISSelectStrains) +
  
  geom_text(data=data_text_Exp, aes(x=450, y=2.8, label=label), colour = "blue", size=3.5) +
  geom_text(data=data_text_St, aes(x=450, y=2.8, label=label), colour = "blue", size=3.5) +
  geom_text(data=data_text_Exp1, aes(x=435, y=2.4, label=label), colour = "blue", size=3.5) +
  geom_text(data=data_text_St1, aes(x=435, y=2.4, label=label), colour = "blue", size=3.5) +
  
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_y_continuous(breaks=seq(0, 3, by = 1)) +
  coord_cartesian(ylim = c(0, 3)) +
  labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  ggh4x::facet_nested(cols = vars(facetsPhase, Phase), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.08,0.87),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.005, "cm"),
        legend.spacing.x = unit(-0.005, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=10))
```


# Create preliminary plot

```{r preliminary plot, fig.height = 8, fig.width = 8}

lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))

OLISSpectraMetaPURMaxAG %>%
  filter(Phase == "Exponential" | Phase == "Pre-stationary") %>% 
  filter(E_days != 1) %>% 
  ggplot() +
  geom_area(aes(x = nm, y = EmNormJaz439), fill = "gray84", alpha = 0.6, show.legend = F) +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain)), show.legend = F, linewidth = 0.7,  alpha = 0.5) +
  # geom_line(aes(x = nm, y = AbsNorm440), show.legend = F, linewidth = 0.5,  colour = "gray20", alpha = 0.7, OLISSelect) +
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_y_continuous(breaks=seq(0, 3, by = 1)) +
  coord_cartesian(ylim = c(0, 3)) +
  labs(y = "Normalized whole-cell absorbance and lamp emission", x = "Wavelength (nm)") +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.08,0.87),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.005, "cm"),
        legend.spacing.x = unit(-0.005, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("SFig_OlisSpectra_Photoperiod",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```

# Create preliminary plot

```{r preliminary plot, fig.height = 8, fig.width = 8}

lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))

OLISSpectraMetaPURMaxAG %>%
  filter(Phase == "Exponential" | Phase == "Pre-stationary") %>% 
  filter(E_days != 1) %>% 
  ggplot() +
  geom_area(aes(x = nm, y = EmNormJaz439), fill = "gray84", alpha = 0.6, show.legend = F) +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain)), show.legend = F, linewidth = 0.7,  alpha = 0.5) +
  # geom_line(aes(x = nm, y = AbsNorm440), show.legend = F, linewidth = 0.5,  colour = "gray20", alpha = 0.7, OLISSelect) +
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_y_continuous(breaks=seq(0, 3, by = 1)) +
  coord_cartesian(ylim = c(0, 3)) +
  labs(y = "Normalized whole-cell absorbance and lamp emission", x = "Wavelength (nm)") +
  ggh4x::facet_nested(cols = vars(facetsPar_ue, Par_ue), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.08,0.87),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.005, "cm"),
        legend.spacing.x = unit(-0.005, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("SFig_OlisSpectra_Light",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```

# Removed unnecessary files from the environment

```{r}
rm(data_text_Exp, data_text_St, data_text_Exp1, data_text_St1, OLISSelectStrains, OLISSelect)
```

# Create tidy df without all nm

```{r clean df, create smaller df - without absorbance and all nm}
OLISAllPURTidy<-OLISSpectraMetaPUR %>% 
  select(-c(Absorbance, nm, Abs440, AbsNorm440, EmJaz439, EmNormJaz439, PURNorm, Emission, SumAbNorm, PURNormSum, SumEmNormJaz439, SumAb, FilenameJaz, EmMax_nm)) %>% 
  unique()

OLISAllPURTidy<-OLISAllPURTidy %>% 
  group_by(Strain, Par_ue, Photoperiod, E_days, MC, Run) %>%
  mutate(PURPARRatio = PUR/Par_ue) %>% 
ungroup()

OLISAllPURTidy <- OLISAllPURTidy %>% 
  mutate(E_hours = E_days*24) %>% 
  filter(PURPARRatio<=1) %>% 
  filter(PURPARRatio>0)
```

# Preparing df for creating plot

```{r create tidy PAR photon dose and facets for plot}
OLISAllPURTidy <- OLISAllPURTidy %>%
    mutate(PARPhotonDoseTidy=PARPhotonDose_day/100000) 

OLISAllPURTidy$facetsPARPhotonDose_day = factor(OLISAllPURTidy$WL, labels = c("PAR~photon~dose~(10^{5}~µmol~photons~m^{-2}~d^{-1})"))
```

# Select variable for choosen PARPhotonDose to create a plot

```{r select variable for choosen PARPhotonDose to create a plot}
tmaxAGSelect<-tmaxAG %>% 
  mutate(PARPhotonDoseTidy=PARPhotonDose_day/100000) %>% 
  filter(PARPhotonDoseTidy == 4.32000|
  PARPhotonDoseTidy == 6.48000|
  PARPhotonDoseTidy == 8.64000|
  PARPhotonDoseTidy == 43.20000|
  PARPhotonDoseTidy == 64.80000|
  PARPhotonDoseTidy == 86.40000) 
```

# Create 4 df for vertical lines (coloured as Strain) contained tMaxAG value

```{r select revelant columns}
tMaxAGLines_056Select<-tmaxAGSelect %>% 
  filter(Strain == "PC-rich_056") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
tMaxAGLines_077Select<-tmaxAGSelect %>% 
  filter(Strain == "PC-rich_077") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
tMaxAGLines_048Select<-tmaxAGSelect %>% 
  filter(Strain == "PE-rich_048") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
tMaxAGLines_127Select<-tmaxAGSelect %>% 
  filter(Strain == "PE-rich_127") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
```

# Create preliminary plot

```{r Create final PUR/PAR ratio plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))

OLISAllPURTidy %>%
  filter(PARPhotonDoseTidy == 4.32000|
  PARPhotonDoseTidy == 6.48000|
  PARPhotonDoseTidy == 8.64000|
  PARPhotonDoseTidy == 43.20000|
  PARPhotonDoseTidy == 64.80000|
  PARPhotonDoseTidy == 86.40000) %>%
  ggplot() +
  geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  geom_vline(data = tMaxAGLines_056Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4", size=0.4) +
  geom_vline(data = tMaxAGLines_077Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3", size=0.4) +
  geom_vline(data = tMaxAGLines_048Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4", size=0.4) +
  geom_vline(data = tMaxAGLines_127Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1", size=0.4) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.5)) +
  ggh4x::facet_nested(cols = vars(facetsPARPhotonDose_day, PARPhotonDoseTidy), labeller = label_parsed) +
  theme_bw()
```

# Removed unnecessary files from the environment

```{r}
rm(tMaxAGLines_056Select, tMaxAGLines_077Select, tMaxAGLines_048Select, tMaxAGLines_127Select, tmaxAG, tmaxAGSelect, OLISSpectraMetaPUR)
```

# Save Fig Rds

```{r}
# saveRDS(OLISSpectraMetaPURShort, file.path(FigRdsPath, paste(Project, "Fig_OlisSpectra_1.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

# saveRDS(OLISSpectraMetaPURMaxAG, file.path(FigRdsPath, paste(Project, "Fig_OlisSpectra_2.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Remove Fig Rds

```{r}
rm(OLISSpectraMetaPURShort)
```

# Save Rds for further analysis

```{r save Rds}
saveRDS(OLISSpectraMetaPURMaxAG, file.path(DataOut, paste(Project, "Processed_OlisSpectraAll.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(OLISAllPURTidy, file.path(DataOut, paste(Project, "Processed_OlisSpectraTidy.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(OLISSpectraMetaPURMaxAG)
```

# Variable names used in Data Dictionary

```{r}
colnames(OLISAllPURTidy)
```

